---
title: "STRAWBERRY_REPORT BY GROUP 8"
author: "Group 8"
date: "11/1/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(magrittr)
library(dplyr)
library(plotrix)
library(wesanderson)

```

# Introduction
After wrangling data, we have the dataset from  only 4 states, which are California, Florida, Oregon and Washington. And we filtered the whole dataset by measured in pounds. By counting the observation grouped by State, we have a map plot, which showed in the California, there are more observations. The question we want to figure out is that bee toxin levels in strawberry chemicals specially in California.

# Map of Distribution of Data

```{r}
## map plot

library(usmap)
library(ggplot2)

state<-c("CALIFORNIA","FLORIDA","OREGON","WASHINGTON")
observation<-c(48,30,4,6)
dataframe <- data.frame(state,observation)
b<-plot_usmap(data = dataframe, values = "observation", color = "blue") + 
  scale_fill_continuous(low = "white", high = "purple",name = "observation", label = scales::comma) + 
  theme(legend.position = "right")
b
```


```{r, echo=FALSE}

## Load data and wrangling data

strawb <- read.csv("Strawberries.csv",fileEncoding = "latin1")

## Drop the no-info columns

drop_no_info_cols <- function(df){
  cnames = colnames(strawb)
  T = NULL
  for(i in 1:ncol(df)){
    T <- c(T, nrow(unique(df[i])))
    }
  drop_cols <- cnames[which(T == 1)]
  return(select(df, !all_of(drop_cols)))
}

strawb <- drop_no_info_cols(strawb)

## Divide "Data.Item" into 4 groups

strawb %<>% separate(col=Data.Item,
                     into = c("Strawberries", "items", "discription", "units"),
                     sep = ",",
                     fill = "right")

## Separate "Domain" into 2 columns

strawb %<>%  separate(col=Domain,
                      into = c("dname", "type" ), 
                      sep = ",", 
                      fill = "right")

## Make a copy of "Domain.Category", called "Chemicals"

strawb %<>% 
  mutate(Chemicals = Domain.Category) %>% 
  relocate(Chemicals, .after = Domain.Category) 

## Vector of logicals for each row with "CHEM" at the start of strawb$Chemicals
## Select "CHEM" from Chemicals"

bb <- strawb$Chemicals %>% str_detect("CHEM")

## Index 

ind_C <- (!bb)*(1:dim(strawb)[1])

## Drop "0" from "ind_C"

r1 <- ind_C[ind_C > 0]

## Set entries in Chemicals column to " " if they don't start with "CHEM"

strawb$Chemicals[r1] <- " "


## Now we need a list of chemicals
## Divide "Chemicals" into 2 groups

strawb %<>% separate(col = Chemicals,
                     into = c("title", "details"),
                     sep = ":",
                     fill = "right")

strawb %<>% mutate(details = str_extract(str_trim(details) ,"[^(].*[^)]") )
strawb %<>% mutate(type = str_trim(type))


strawb_chem <- strawb %>% filter((type=="FUNGICIDE")|
                                   (type=="HERBICIDE")|
                                   (type=="INSECTICIDE"))

strawb_other <- strawb %>% filter(type=="OTHER")

strawb_na <- strawb %>% filter(is.na(type)==TRUE)


pesticides <- read_csv("Pesticides(1).csv",show_col_types = FALSE)


#Delete "N/A" from "Pesticide"

pesticides <- filter(pesticides, !is.na(Pesticide))

#Delete "N/A" from "details"

strawb_new <- filter(strawb, !is.na(details))

## Divide "details" into 2 groups

strawb_new %<>% separate(col = details, 
                            into = c("chemical_name", "chemical_id"), 
                            sep = "=", 
                            fill = "right")

#Capitalization of the "Pesticide" so that it matches the the dataset "strawb"

pesticides <- mutate(pesticides, Pesticide = toupper(Pesticide))

#trimws: Deletes leading/trailing Spaces

strawb_new <- mutate(strawb_new, chemical_name = trimws(chemical_name))

## join two dataframe

joined <- inner_join(strawb_new, pesticides, 
                     by = c("chemical_name" = "Pesticide"))


## select column

joined_new<-select(joined,Year,State,discription,type,chemical_name,Value, Carcinogen,"Hormone Disruptor",Neurotoxins,"Developmental or Reproductive Toxins","Bee Toxins")


```
\pagebreak
# Exploratory data analysis

First, we created a barplot grouped by state shows the value of bee toxin levels, with years combined. 
We can see that we have most data observations in California.

```{r}
#names(joined)[4] <- "Measurement(s)"

joined_new <- data.frame(joined_new)
#view(cal_data)
Bee.toxins_LB <- subset(joined_new, discription==" MEASURED IN LB")
Bee.toxins <- subset(Bee.toxins_LB, Bee.Toxins != "")

plot <- ggplot(Bee.toxins, aes(x = State, y = Value, fill = Bee.Toxins)) +
  geom_col(position = "dodge", colour = "black") +
  scale_fill_brewer(palette = "Pastel1")
plot
```

\pagebreak
# Pie Plots

The pie plots show in different years and states the percentage of chemicals with different levels of bee toxins. 
it shows the variance of bee toxin.

```{r}
## Divide by "Year"(only have 2019\2018\2016),explore every "Year" by "State"

joined_new_2019 <- joined_new[joined_new$Year == 2019, ] 
#table(joined_new_2019$State)
joined_new_2018 <- joined_new[joined_new$Year == 2018, ] 
#table(joined_new_2018$State)
joined_new_2016 <- joined_new[joined_new$Year == 2016, ] 
#table(joined_new_2016$State)

## Divide by region in different "Year"

joined_new_2019_CALIFORNIA <- joined_new_2019[joined_new_2019$State=="CALIFORNIA",]
#table(joined_new_2019_CALIFORNIA$"Bee Toxins")
joined_new_2019_FLORIDA <- joined_new_2019[joined_new_2019$State=="FLORIDA",]
#table(joined_new_2019_FLORIDA$"Bee Toxins")

joined_new_2018_CALIFORNIA <- joined_new_2018[joined_new_2018$State=="CALIFORNIA",]
#table(joined_new_2018_CALIFORNIA$"Bee Toxins")
joined_new_2018_FLORIDA <- joined_new_2018[joined_new_2018$State=="FLORIDA",]
#table(joined_new_2018_FLORIDA$"Bee Toxins")

joined_new_2016_CALIFORNIA <- joined_new_2016[joined_new_2016$State=="CALIFORNIA",]
#table(joined_new_2016_CALIFORNIA$"Bee Toxins")
joined_new_2016_FLORIDA <- joined_new_2016[joined_new_2016$State=="FLORIDA",]
#table(joined_new_2016_FLORIDA$"Bee Toxins")
joined_new_2016_OREGON <- joined_new_2016[joined_new_2016$State=="OREGON",]
#table(joined_new_2016_OREGON$"Bee Toxins")
joined_new_2016_WASHINGTON <- joined_new_2016[joined_new_2016$State=="WASHINGTON",]
#table(joined_new_2016_WASHINGTON$"Bee Toxins")

## pie plot in CALIFORNIA
par(mfrow = c(1, 3)) # Create a 1 x 3 plotting matrix

freq<-c(30,15,35)
piepercent<- paste(round(100*freq/sum(freq), 2), "%")
pie1=pie(freq,labels = piepercent,main="2016_CALIFORNIA",col = terrain.colors(length(freq)),edges = 200, radius = 1)

freq<-c(30,15,35)
piepercent<- paste(round(100*freq/sum(freq), 2), "%")
pie1=pie(freq,labels = piepercent,main="2018_CALIFORNIA",col = terrain.colors(length(freq)),edges = 200, radius = 1)

freq<-c(30,15,35)
piepercent<- paste(round(100*freq/sum(freq), 2), "%")
pie1=pie(freq,labels = piepercent,main="2019_CALIFORNIA",col = terrain.colors(length(freq)),edges = 200, radius = 1)

legend("bottom",c("high","moderate","slight"),cex=1,fill=terrain.colors(length(freq)))


## pie plot in FLORIDA
 par(mfrow = c(1, 3))# Create a 1 x 3 plotting matrix

freq<-c(15,15,25)
piepercent<- paste(round(100*freq/sum(freq), 2), "%")
pie1=pie(freq,labels = piepercent,main="2016_FLORIDA",col = terrain.colors(length(freq)),edges = 200, radius = 1)

freq<-c(15,10,15)
piepercent<- paste(round(100*freq/sum(freq), 2), "%")
pie1=pie(freq,labels = piepercent,main="2018_FLORIDA",col = terrain.colors(length(freq)),edges = 200, radius = 1)

freq<-c(20,10,25)
piepercent<- paste(round(100*freq/sum(freq), 2), "%")
pie1=pie(freq,labels = piepercent,main="2019_FLORIDA",col = terrain.colors(length(freq)), edges = 200, radius = 1)

legend("bottomleft",c("high","moderate","slight"),cex=1,fill=terrain.colors(length(freq)))

## pie plot in OREGON & WASHINGTON
par(mfrow = c(1, 3))

freq<-c(10,0,10)
piepercent<- paste(round(100*freq/sum(freq), 2), "%")
pie1=pie(freq,labels = piepercent,main="2016_OREGON",col = terrain.colors(length(freq)),edges = 200, radius = 1)

freq<-c(10,5,15)
piepercent<- paste(round(100*freq/sum(freq), 2), "%")
pie1=pie(freq,labels = piepercent,main="2016_WASHINGTON",col = terrain.colors(length(freq)),edges = 200, radius = 1)
legend("bottomright",legend=c("high","moderate","slight"),cex=0.4,fill=terrain.colors(length(freq)))
       


```

\pagebreak

# Scatter Plots

First, we have5 scatter plots show the splits among the measurement groups, which are measured in LB, measured in LB/ACRE/APPLICATION, measured in LB/ACRE/YEAR,measured in NUMBER and measured in PCT of AREA BEARING.
After we decided to focus on the measured in LB and bee toxins, we have 4 scatter plots that stratify state against bee toxin level.



```{r,echo=FALSE,message=FALSE, warning=FALSE}

#Jack's point plot

names(joined)<-make.names(names(joined),unique = TRUE)
joined$Value <- as.numeric(gsub(",", "",joined$Value))

groups <- unique(joined$discription)
for (group in groups){
  df <- filter(joined, discription == group)
  print(ggplot(data = df) + 
    geom_jitter(mapping = aes(x = Bee.Toxins, y=Value, color = Bee.Toxins), size = 3)+
      ggtitle(group))
}

states <- unique(joined$State)
for (state in states){
  df <- filter(joined, State == state, discription == " MEASURED IN PCT OF AREA BEARING")
  print(ggplot(data = df) + 
          geom_jitter(mapping = aes(x = Bee.Toxins, y=Value, color = Bee.Toxins), size = 3)+
          ggtitle(state))
}
```
\pagebreak

# Bee Safe Program

In the mean time, we found out an article about the California State law named Bee safe program, 
which related to bees and pesticides. https://lao.ca.gov/Publications/Report/3793

This State law requires that begin in 2018-2019, any person intending to apply any pesticide labeled “toxic to bees” to a blossoming plant to ask the local CAC, or designee, whether there are registered beekeepers with colonies located within a one-mile radius of the application site. The CAC provides the pesticide applicator with the contact information of registered beekeepers who wish to be notified in the affected areas. 

We would like to know that whether the State Law made the strawberry farmers think that there is a lot of work to worry and they decided use less toxicity pesticides or in the other way.

# Stacked Barplot

The stacked barplot shows percentage of use in terms of bee toxins based on the level over all 3 years.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# deal with pesticides1
pesticides <- pesticides %>% 
  filter(!is.na(Pesticide))
pesticides <- pesticides %>% 
  mutate(Pesticide = toupper(Pesticide))
pesticides1 <- pesticides %>% 
  rename(chemical_name = Pesticide)

# deal with joined2
# install.packages("prob")
joined2 <- left_join(strawb_new, pesticides1,
                     by = "chemical_name")

# subset by state
california <- joined2 %>% 
  filter(State == "CALIFORNIA")
florida <- joined2 %>% 
  filter(State == "FLORIDA")
oregon <- joined2 %>% 
  filter(State == "OREGON")
washington <- joined2 %>% 
  filter(State == "WASHINGTON")

# subset by chemical type
cali_chem <- california %>% filter((type=="FUNGICIDE")|
                                   (type=="HERBICIDE")|
                                   (type=="INSECTICIDE"))
cali_other <- california %>% filter(type=="OTHER")

# subset by no chemical
cali_na <- california %>% filter(is.na(type)==TRUE)

# chemical data are classified according to year,unit of measurement,chemical type
cali_chem1 <- cali_chem %>% 
  group_by(Year, type, discription) %>% 
  summarise(count = n())

# value as.numeric
cali_chem$Value <- as.numeric(cali_chem$Value)

# sum
cali_chem1 <- cali_chem %>% 
  group_by(Year, type, discription) %>% 
  summarise(count = n(), value_sum = sum(Value))

# measured in lb larger than other units of measurement
aa <- !is.na(cali_chem$`Bee Toxins`)
ind_C1 <- (!aa)*(1:dim(cali_chem)[1])
r2 <- ind_C1[ind_C1>0]
cali_chem$`Bee Toxins`[r2] <- "none"

cali_chem_summary <- cali_chem %>% 
  group_by(Year,`Bee Toxins`) %>% 
  summarise(total_usage = sum(Value, na.rm = T))

# change position of slight,none
yy <- factor(as.factor(cali_chem_summary$`Bee Toxins`), levels = c("none", "slight" , "moderate", "high"))

cali_chem_summary$`Bee Toxins` <- yy

cali_chem_summary_ordered <- cali_chem_summary %>% 
  arrange(Year,`Bee Toxins`)

# total usage every year
cali_chem_summary1 <- cali_chem_summary %>% 
  group_by(Year) %>% 
  summarise(useageofyear = sum(total_usage))

# Bee toxicity of high, medium and low without use, percentage
perc_col = matrix(cbind(cali_chem_summary_ordered$total_usage[1:4] / 6046.092 , cali_chem_summary_ordered$total_usage[5:8] / 9177.122, cali_chem_summary_ordered$total_usage[9:12] / 8457.764), nrow = 12)

cali_chem_summary_ordered$percentage <- perc_col

#stacked plot
ggplot(cali_chem_summary_ordered, aes(fill = `Bee Toxins`, y = percentage, x = Year)) + 
  geom_bar(position="stack", stat="identity")+ scale_fill_brewer(palette = "Pastel1")
```

# Conclusion

Since we focus on the Bee Safe Program in California, based on th purple bar, we do can see that the percentage of the pesticide's usage which included high bee toxins is decreasing. Therefore, we roughly draw a conclusion that the Bee Safe Program indeed In the future, we should analyze more related data sets and give a more accurate conclusion.

