---
output: 
  revealjs::revealjs_presentation:
    theme: black
    highlight: pygments 
    css: reveal.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<section data-background-opacity=0.2
         data-background-image="Strawberry-Bee.jpg">
   <h1 style="margin-top:35px;text-align:center;color=black;font-family:verdana;font-size:50px;">
Group 8: Bee Toxin Levels in Strawberry Chemicals</h1>

<p style="margin-top:475px;text-align:center;font-family:verdana;font-size:35px;color=black">Yujia Wang, Jack Carbaugh, Xiang Li, Danny Zhang</p>

#### image source --  https://ucanr.edu/blogs/blogcore/postdetail.cfm?postnum=4816

</section>

## Map of Distribution of Data

```{r, echo=FALSE, message= FALSE, warning = FALSE}
source(file = "PDF_REPORT.R", echo = FALSE)
freq_map()
```

## Measurement Exploration

```{r, echo=FALSE, out.width = "33%", message= FALSE, warning = FALSE}
source(file = "PDF_REPORT.R", echo = FALSE)
plot_Measurements(joined)
```

## Stratifying by State

```{r, echo=FALSE, out.width = "33%", out.height="50%", message= FALSE, warning = FALSE}
source(file = "PDF_REPORT.R", echo = FALSE)
plot_Points(joined)
plot_Cols(joined)
```

## Stratifying by State and Year

```{r, echo=FALSE, out.width = "50%", message= FALSE, warning = FALSE}
source(file = "PDF_REPORT.R", echo = FALSE)
plot_Pies(joined)
```

## Focus: Bee Safe Program
<p style="margin-top:175px;text-align:center;font-family:verdana;font-size:35px;color=black"> During the course of our EDA, we found an article about a recent law in California: the Bee Safe Program </p>

<p style="margin-top:175px;text-align:center;font-family:verdana;font-size:35px;color=black"> Beginning in 2018-2019, any person intending to use a pesticide labeled "toxic to bees" to a blossoming plant had to contact local beekeepers within a 1 mile radius </p>


## Stratifying by State and Year

```{r, echo=FALSE, out.width = "50%", message= FALSE, warning = FALSE}
source(file = "PDF_REPORT.R", echo = FALSE)
plot_Pies(joined)
```





