---
output: 
  revealjs::revealjs_presentation:
    theme: black
    highlight: pygments 
    css: reveal.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<section data-background-opacity=0.2
         data-background-image="Strawberry-Bee.jpg">
   <h1 style="margin-top:35px;text-align:center;color=black;font-family:verdana;font-size:50px;">
Group 8: Bee Toxin Levels in Strawberry Chemicals</h1>

<p style="margin-top:535px;text-align:center;font-family:verdana;font-size:35px;color=black">Yujia Wang, Jack Carbaugh, Xiang Li, Handing Zhang</p>

#### image source --  https://ucanr.edu/blogs/blogcore/postdetail.cfm?postnum=4816

</section>

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

