---
title: "PDF_REPORT BY GROUP 8"
author: "Group 8"
date: "11/1/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(magrittr)
library(dplyr)
library(plotrix)
library(wesanderson)
```

# Introduction
After wrangling data, we have the dataset from  only 4 states, which are California, Florida, Oregon and Washington. And we filtered the whole dataset by measured in pounds. By counting the observation grouped by State, we have a map plot, which showed in the California, there are more observations. 
```{r,message= FALSE, warning = FALSE}

source(file = "DataWrangling_and_Visualization.R", echo = FALSE)
freq_map()

```



# Exploratory data analysis
This barplot grouped by state shows the value of bee toxin levels, with years combined. 
We can see that we have most data observations in California.

```{r,message= FALSE, warning = FALSE}
plot_Cols(joined)
```

# Pie Plots

The pie plots show in different years and states the percentage of different levels of bee toxins.
it shows the variance of bee toxin. Can show difference in states and years.
Map with 4 states showing how much of the chemical is being used.

```{r,message= FALSE, warning = FALSE}
plot_Pies(joined)
```

# Scatter Plots

5 scatter plots show the splits amongst the measurement groups and 5 scatter plots that stratify state against bee toxin level

```{r,echo=FALSE,message=FALSE, warning=FALSE}
#Jack's point plot
plot_Points(joined)
```

# Bee Safe Program

In the mean time, we found out an article about the California State law named Bee safe program,
which related to bees and pesticides. https://lao.ca.gov/Publications/Report/3793

This State law requires that begin in 2018-2019, any person intending to apply any pesticide labeled “toxic to bees” to a blossoming plant to ask the local CAC, or designee, whether there are registered beekeepers with colonies located within a one-mile radius of the application site. The CAC provides the pesticide applicator with the contact information of registered beekeepers who wish to be notified in the affected areas.

Stacked Barplot showing percentage of use in terms of bee toxins based on the level over all 3 years.

```{r,echo=FALSE,message=FALSE, warning=FALSE}
source(file = "DataWrangling_and_Visualization.R", echo = FALSE)
plot_bar(cali_chem_summary_ordered)
plot_stacked_bar(cali_chem_summary_ordered)
```

